% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2010 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage[hide links]{hyperref}
\definecolor{mygrey}{RGB}{112,183,224}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Matthew D. Robertson}  & xxx.xxx.xxxx (cell phone)\\
Address1&  \href{mailto:iam@mattrobertson.ca}{iam@mattrobertson.ca} \\
Address2& \url{http://mattrobertson.ca}\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Summary of Qualifications}
\begin{itemize}
	\resitem{Proficient with Python, C++, AngularJS, Java, C, Ubuntu, Git, and \LaTeX. Functional knowledge of OpenGL, GLSL, SQL, PostgreSQL, Jenkins, Jira,  and SVN. }
	\resitem{Four years experience as a core member of a small video game development team, focusing on engine design and implementation in the Object-Oriented paradigm.}
	\resitem{Possesses excellent problem solving, communication, interpersonal, and organizational skills developed through past work experience.}	
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item \ressubheading{Autodesk}{Montr\'eal, QC}{Maya Foundation, Software Development Co-op}{September 2016 - December 2016}
	\begin{itemize}
		\resitem{Integrated Pixar's Universal Scene Description plug-in into Maya, allowing other teams to further make use of USD in their development.}
		\resitem{Developed scripts to convert scenes from Autodesk's Hyperspace Madness into USD files, reducing load times significantly.}
	\end{itemize}
\item \ressubheading{Intel Security}{Waterloo, ON}{Software Development Engineer}{January 2016 - April 2016}
	\begin{itemize}
		\resitem{Resolved software problems in the Intel Security product line, including one which prevented the successful installation of the product.}
		\resitem{Created and repaired Jenkins jobs to ensure the accuracy of test coverage metrics and proper deployment of builds.}
	\end{itemize}
\item \ressubheading{RideCo}{Waterloo, ON}{Software Developer}{May 2015 - August 2015}
	\begin{itemize}
		\resitem{Developed and simplified tools to allow administrators to quickly and easily create and visualize optimized vehicle schedules, for the efficient solving of custom vehicle routing problems.}
		\resitem{Improved tools used by administrators to analyze user data in real-time.}
	\end{itemize}
\item \ressubheading{Bayer Radiology and Interventional}{Toronto, ON}{Software Developer}{May 2014 - August 2014}
	\begin{itemize}
		\resitem{Developed software for estimating and tracking radiation exposure in medical imaging as well as interfaces for consumption of derived data. }
		\resitem{Engineered a higher performance ActionScript scatter-plot. This reduced runtime from up to eleven seconds for datasets with upwards of ten thousand points down to under three seconds.}
	\end{itemize}
\end{itemize}

\resheading{Projects}
\begin{itemize}
\item
	\ressubheading{Pixel Shaders and Demoscene}{\url{https://www.shadertoy.com/user/twitchingace}}{Lead Developer}{June 2014 - Present}
	\begin{itemize}
		\resitem{Created a number of pixel shaders built on the concept of "two-triangle rendering." Scenes created entirely inside the shader.}
		\resitem{Created a distance-field based ray marcher for the purpose of rendering and blending geometric three-dimensional shapes.}
		\resitem{Created a basic ray tracer as a foray into the technique.}
	\end{itemize}
\newpage
\item
	\ressubheading{Terrae Rasa}{\url{https://github.com/matthew-robertson/Terrae-Rasa}}{Lead Developer}{January 2012 - September 2013}
	\begin{itemize}
		\resitem{Worked as a lead developer and as a lead designer on a two-dimensional side-on adventure game.}
		\resitem{Designed techniques which I used to procedurally generate random worlds of arbitrary size, while still ensuring the playability and enjoyability of the game world.}
		\resitem{Developed an elementary physics-based particle engine for the handling of generic particle effects and projectiles.}
		\resitem{Implemented a state-based AI with functionality to chase, retreat, or attack based on its environment.}
	\end{itemize}
\end{itemize}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{University of Waterloo}{Waterloo, ON}{Candidate for Bachelor of Mathematics in Computer Science. Honours Co-op}{September 2013 - Present}
	\begin{itemize}
		\resitem{Current 3B student, graduation anticipated for 2018.}
		\resitem{$72.1\%$ cumulative average, $73.8\%$ major average.}	
	\end{itemize}

\end{itemize}

\resheading{Awards}
\begin{description}
\item
	\ressubheading{New Brunswick Computer Science Competition 2\textsuperscript{nd} place.}{2013}{}{}
\item
	\ressubheading{University of Waterloo Euclid Mathematics Competition top 20\%.} {2013} {} {}

\item
\ressubheading{New Brunswick Computer Science Competition 3\textsuperscript{rd} place.}{2012}{}{}
\item
\ressubheading{University of Waterloo Canadian Computing Competition honour roll.}{2012}{}{}
\end{description}

\end{document}
